Thesis: draft

### 2021-03-25 draft.tex
continued working on lay-out

@@

\usepackage{wrapfig}              % meer controle over figuren
\usepackage{floatrow}
\usepackage[format=hang]{caption}
\usepackage{listings}                   % voor mooie code
\usepackage{amsmath, amssymb, amsfonts} % om wiskunde te typen
\usepackage{scalerel}                   % om symbolen te schalen
\let\proof\relax
\let\endproof\relax
\usepackage{amsthm}
\usepackage{bm}                         % Wiskundesymbolen vet met commando \bm{}
\usepackage{libertine}                  % lettertype
\usepackage{inconsolata}                % lettertype code
\usepackage[T1]{fontenc}                % betere lettertype encodering voor talen met accenten
\usepackage{setspace}
\usepackage{enumitem}
\usepackage{units}
\usepackage{multicol}
\usepackage{appendix}
\usepackage{titlesec}
\usepackage{bbold}
\usepackage{algorithm}
\usepackage{physics}
\usepackage{interval}
\usepackage[colorlinks,citecolor=red,urlcolor=blue,bookmarks=false,hypertexnames=true]{hyperref} 
\usepackage[noend]{algpseudocode}
\usepackage{subcaption}
\usepackage{xfrac}
\floatname{algorithm}{Algoritme}

@@

\begin{document}
\frontmatter

@@

\pagestyle{fancy}
\fancyhf{}
\lhead{\chaptername \ \thechapter}
\rhead{\rightmark}
\cfoot{\thepage}

@@

\pagestyle{fancy}
\fancyhf{}
\lhead{\appendixname \ \thechapter}
\rhead{\rightmark}
\cfoot{\thepage}

>>>>

\usepackage[dvipsnames]{xcolor}

@@

\usepackage{wrapfig}              % meer controle over figuren
\usepackage{floatrow}
\usepackage[format=hang]{caption}
\usepackage{listings}                   % voor mooie code
\usepackage{amsmath, amssymb, amsfonts} % om wiskunde te typen
\usepackage{scalerel}                   % om symbolen te schalen
\let\proof\relax
\let\endproof\relax
\usepackage{amsthm}
\usepackage{bm}                         % Wiskundesymbolen vet met commando \bm{}
\usepackage{libertine}                  % lettertype
\usepackage{inconsolata}                % lettertype code
\usepackage[T1]{fontenc}                % betere lettertype encodering voor talen met accenten
\usepackage{setspace}
\usepackage{enumitem}
\usepackage{units}
\usepackage{multicol}
\usepackage{appendix}
\usepackage{titlesec}
\usepackage{bbold}
\usepackage{algorithm}
\usepackage{physics}
\usepackage{interval}
\usepackage[colorlinks,citecolor=NavyBlue,linkcolor=NavyBlue% 
,urlcolor=NavyBlue,linktocpage=true,bookmarks=false,hypertexnames=true]{hyperref} 
\usepackage[noend]{algpseudocode}
\usepackage{subcaption}
\usepackage{xfrac}
\floatname{algorithm}{Algoritme}

@@

\usepackage{sectsty}

\chapternumberfont{\color{NavyBlue}}
\chaptertitlefont{\color{black}\sectionrule{3ex}{3pt}{-1ex}{1pt}}

\begin{document}

\frontmatter
\selectlanguage{english}

\begin{titlepage}
\begin{center}

\vspace*{.06\textheight}
{\scshape\LARGE \textcolor{NavyBlue}{Ghent University}\par}\vspace{1.5cm} % University name
\textsc{\Large Master Thesis}\\[0.5cm] % Thesis type

\hrule % Horizontal line
\vspace{0.4cm} 
{\huge \bfseries Opinion dynamics on social media with stubborn actors\par}\vspace{0.4cm} % Thesis title
\hrule % Horizontal line
\vspace{1.5cm}

\begin{minipage}[t]{0.4\textwidth}
\begin{flushleft} \large
\emph{Author:}\\
\textcolor{NavyBlue}{Nina \textsc{Botte}} % Author name - remove the \href bracket to remove the link
\end{flushleft}
\end{minipage}
\begin{minipage}[t]{0.4\textwidth}
\begin{flushright} \large
\emph{Supervisor:} \\
\textcolor{NavyBlue}{Prof. Dr. Luis E.C. \textsc{Rocha}} % Supervisor name - remove the \href bracket to remove the link  
\end{flushright}
\end{minipage}\\[3cm]

\vfill

\large \textit{A thesis submitted in partial fulfillment of the requirements\\ for the degree of Master of Science in Physics and Astronomy}\\[0.3cm] % University requirement text
\textit{in the}\\[0.4cm]
\textcolor{NavyBlue}{Faculty of \textsc{Science}}\\\textcolor{NavyBlue}{Department of \textsc{Physics and Astronomy}}\\[2cm] % Research group name and department name

\vfill

{\large \today}\\[4cm] % Date
%\includegraphics[scale=0.7]{ugent_logo.png} % University/department logo - uncomment to place it

\vfill
\end{center}
\end{titlepage}

@@

\pagestyle{fancy}
\fancyhf{}
\lhead{\textcolor{NavyBlue}{\chaptername} \ \textcolor{NavyBlue}{\thechapter}}
\rhead{\rightmark}
\cfoot{\thepage}

@@

\pagestyle{fancy}
\fancyhf{}
\lhead{\textcolor{NavyBlue}{\appendixname} \ \textcolor{NavyBlue}{\thechapter}}
\rhead{\rightmark}
\cfoot{\thepage}
